% Synthetic test fixture for rw-screen.
% Authors and venue are fictional; the bibliography below references THREE
% real Retraction Watch records by DOI to verify reference-side detection.

A Survey on Adversarial Robustness in Modern Neural Networks

Alice Doe, Bob Smith, Charlie Park

Department of Computer Science, Imaginary University, Wonderland

Keywords: adversarial, robustness, neural networks

\section{Introduction}
This paper reviews recent advances in adversarial robustness for deep neural
networks, with a focus on certified defenses and randomized smoothing.

\section{Background}
We build on prior work in image classification and machine learning systems.

\section{Discussion}
The strengths and weaknesses of existing approaches are summarized.

\begin{thebibliography}{99}
\bibitem{maqsoom2022} Ahsen Maqsoom, Bilal Aslam, Arbaz Yousafzai, Fahim Ullah, Sami Ullah, Muhammad Imran. Extracting built-up areas from spectro-textural information using machine learning. \emph{Soft Computing}, 2022. doi:10.1007/s00500-022-06794-6
\bibitem{khan2022} Fakhri Alam Khan, Kifayat Ullah, Atta ur Rahman, Sajid Anwar. Energy optimization in smart urban buildings using bio-inspired ant colony optimization. \emph{Soft Computing}, 2022. doi:10.1007/s00500-022-07537-3
\bibitem{girdhar2022} Nancy Girdhar, Aparna Sinha, Shivang Gupta. DenseNet-II: an improved deep convolutional neural network for melanoma cancer detection. \emph{Soft Computing}, 2022. doi:10.1007/s00500-022-07406-z
\bibitem{vaswani2017} Ashish Vaswani, Noam Shazeer, Niki Parmar, et al. Attention is All You Need. \emph{NeurIPS}, 2017.
\bibitem{he2016} Kaiming He, Xiangyu Zhang, Shaoqing Ren, Jian Sun. Deep Residual Learning for Image Recognition. \emph{CVPR}, 2016.
\end{thebibliography}
